---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cowgillr

<!-- badges: start -->
[![R-CMD-check](https://github.com/MattCowgill/cowgillr/workflows/R-CMD-check/badge.svg)](https://github.com/MattCowgill/cowgillr/actions)
<!-- badges: end -->

cowgillr is a package that allows me to get set up in a new R install quickly. It installs key packages and their dependencies, sets up `Makevars` and `.Rprofile` the way I want them, installs fonts, and sets RStudio light and dark themes. 

cowgillr is not intended for use by anyone other than me.

## Installation

You can install the development version of cowgillr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("MattCowgill/cowgillr")
```

## Set up an R install

```{r example, eval=FALSE}
library(cowgillr)
cowgill_setup()
```
